Improving the Apollo 12 landing site mapping\\with Chandrayaan $M^3$ data

### 2014-04-21 grassposter/2014_EGU_M3_Landscape/poster.tex
updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59877 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{center}
 \includegraphics[width=0.75\textwidth]{./images/Clementine}
 \newline
 Figure 1: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
\end{center}
}

@@

\begin{center}
\begin{tabular}{ c p{0.45\textwidth}}
 \raisebox{-0.8\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1}}
 %\caption{Testing FeO algorithms.}
 \label{fig:FeOtesting}
 &
 \noindent It is known that the local range of FeO is below 10wt\% from UVVIS data (see Figure on the lower left), only the Lawrence et al. (2002) equation is giving an appropriate range. Lucey et al. (2000) equation fails because of the offset of uvvis4/uvvis2(=1.15 vs offset = 1.19) and the one for uvvis2(=0.05 vs offset = 0.08), as both of the parts are negative thus giving a positive division output, their interplay should bring a negative number for the arctangent negative sign to compensate. This clearly does not happen with $M^3$ data in the Bench and Surveyor craters, the results from the arctangent being positive, and the sign change brings the main part of the equation to a negative, further reduced by the negative final offset.\newline
\end{tabular}
\end{center}
\noindent Upon using the  Lawrence et al. (2002) equation, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
\noindent The equation from Zhang et al. (2013) is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.\newline

>>>>

\begin{center}
 \includegraphics[width=0.75\textwidth]{./images/Clementine}
 \newline
 Figure 2: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
\end{center}
}

@@

\begin{center}
\begin{tabular}{ c p{0.45\textwidth}}
 \raisebox{-0.8\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1}}
 %\caption{Testing FeO algorithms.}
 \label{fig:FeOtesting}
 &
 \noindent It is known that the local range of FeO is below 10wt\% from UVVIS data (see Figure on the lower left), only the Lawrence et al. (2002) equation is giving an appropriate range. Lucey et al. (2000) equation fails because of the offset of uvvis4/uvvis2(=1.15 vs offset = 1.19) and the one for uvvis2(=0.05 vs offset = 0.08), as both of the parts are negative thus giving a positive division output, their interplay should bring a negative number for the arctangent negative sign to compensate. This clearly does not happen with $M^3$ data in the Bench and Surveyor craters, the results from the arctangent being positive, and the sign change brings the main part of the equation to a negative, further reduced by the negative final offset.\newline
\end{tabular}
\end{center}
\noindent Upon using the  Lawrence et al. (2002) equation, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
\noindent The equation from Zhang et al. (2013) is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values. Comparing the zonal contrast between Clementine FeO map from Lucey et al. (2000) the $M^3$ from Zhang et al. (2013) leads to an interesting prospect as even the shapes are not consistent (see Figures ~\ref{fig:subfeoclem} \& ~\ref{fig:subfeoM3}). This indicates that the inner work of the angle equation is not sensitive to the same type of distance between R950 and R750 as they are in Clementine and in $M^3$. In an ideal condition, the calibration of both sensor bands would be identical, and the sensor response for each band would also be the same. This is not a reality, from the design and manufacture inheritance of multi-spectral sensors and hyperspectral sensors, to the data collection flight and its environment. Finally, some accident or issues can damage the operation.\newline

\begin{center}
 \includegraphics[width=0.4\textwidth,keepaspectratio=true]{./images/Clem_FeO_area}
% \caption{Subset of Clementine FeO using \citep{lucey2000lunar}}
 \label{fig:subfeoclem}
\hspace{5mm}
 \includegraphics[width=0.435\textwidth,keepaspectratio=true]{./images/M3_Zhang_FeO_area}
% \caption{Subset of $M^3$ FeO using \cite{zhang2013mapping}}
 \label{fig:subfeoM3}
\end{center}
